Typed Clojure

### 2014-11-21 formal-model.tex
fixes after meeting

says expression \e{} is of type \t{} in the 
multimethod environment $\trdiff{\mmenv{}}$, the \emph{tools.analyzer} environment
$\trdiff{\taenv{}}$
and proposition environment $\propenv{}$, with 
then proposition {\thenprop {\prop{}}}, else proposition {\elseprop {\prop{}}},
object \object{} and new multimethod environment
$\trdiff{\mmenvp{}}$.

>>>>

says expression \e{} is of type \t{} in the 
proposition environment $\propenv{}$, with 
then proposition {\thenprop {\prop{}}}, else proposition {\elseprop {\prop{}}}
and object \object{}.
